The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-10-18 paper.qmd
added comment for package install

# load Libraries
library(tidyverse)
library(Vizumap)
library(RColorBrewer)
library(scales)
library(sf)
library(ggrepel)
library(urbnmapr)
library(flextable)
library(colorspace)
library(rgeos)
```

>>>>

# load Libraries
library(tidyverse)
# devtools::install_github("lydialucchesi/Vizumap")
library(Vizumap)
library(RColorBrewer)
library(scales)
library(sf)
library(ggrepel)
# devtools::install_github("UrbanInstitute/urbnmapr")
library(urbnmapr)
library(flextable)
library(colorspace)
library(rgeos)
```
